Read Me

### 2020-05-15 readme.Rmd
Lab work notes last day in Ås

#Lab-Notes
Samples 2020-02-13
Vial  Sample         Pinus  Betula  Salix  Spores
5*    A4-DL 138-140  +++    +              +++
4     D4-DL 161-163  ++     +              +++
4*    A5-UR  64- 66  ++     +       1      +++

@@

Samples 2020-02-19
Vial  Samples
1     TSK15-K6 42.0-42.8
2*    TSK15-K6 17.5-18.2
3*    TSK15-K6 38.7-39.2
4*    TSK15-K6  9.8-10.5
4     TSK15-K6 26.0-26.8
5     TSK15-K6  0.0- 1.5
5*    TSK15-K6 14.0-14.5
6     TSK15-K6 34.0-35.0
7     TSK15-K6 29.5-31.0
8     TSK15-K6 21.5-22.2

@@

>>>>

#Lab-Notes
##Samples 2020-02-13
Vial  Sample         Pinus  Betula  Salix  Spores
5*    A4-DL 138-140  +++    +              +++
4     D4-DL 161-163  ++     +              +++
4*    A5-UR  64- 66  ++     +       1      +++

@@

##Samples 2020-02-19
Vial  Samples
1     TSK15-K6 42.0-42.8
2*    TSK15-K6 17.5-18.2
3*    TSK15-K6 38.7-39.2
4*    TSK15-K6  9.8-10.5
4     TSK15-K6 26.0-26.8
5     TSK15-K6  0.0- 1.5
5*    TSK15-K6 14.0-14.5
6     TSK15-K6 34.0-35.0
7     TSK15-K6 29.5-31.0
8     TSK15-K6 21.5-22.2

##Samples 2020-05-04
Urio Zuazzrocchi
Vial  Samples
1     UQC-20
2     UQC-70
2*    UQC-150
3*    UQC-268
4     UQC-365
5*    UQC-468
6     UQC-588
7     UQC-667
8     UQC-767
8*    UQC-882

Notes: after first waterwash vial 5-8 spilled in the centrifuge

##Samples 2020-05-05
Sa Curcurica
Vial  Samples
1     SCUR-12
2     SCUR-120
2*    SCUR-232
3*    SCUR-328
4     SCUR-430
5*    SCUR-526
6     SCUR-664
7     SCUR-728
8     SCUR-824
8*    SCUR-944

##Samples 2020-05-06
Lago del Sangiatto
Vial  Samples
1     SNG-32
2     SNG-72
2*    SNG-128
3*    SNG-176
4     SNG-224
5*    SNG-264
6     SNG-308
7     SNG-328
8     SNG-360
8*    SNG-390

##Samples 2020-05-07
Dalmutladdo
Vial  Samples
1     DL-20
2     DL-40
2*    DL-60
3*    DL-90
4     DL-100
5*    DL-110
6     DL-120
7     DL-130
8     DL-140
8*    DL-150

@@

#Ås Labwork

2020-05-11
Bergen PS7_02
all sideways pollen
polar pollen left 2x2

INN_PS3_01
sideways pollen: all
polar pollen: 1x1 and 1x2

INN_PS19_01
sideways_pollen: 1x1, 1x3
polar pollen: 1x1,1x2

DAL_20_01
all Pinus
Alnus (6)
BetCor (8)

DAL_20_02
all Pinus
Alnus (1)
BetCor (7)

BGO_PS08
sideways: 25 grains
polar: 25 grains

DAL_90_01
all Pinus (8)
blanks (6)

DAL_90_02
all Pinus (9)
blanks (6)

DAL_90_03
all Pinus (19)
blanks (6)

DAL_130_01
all Pinus (12)
blanks (6)

DAL_130_02
all Pinus (27)
blanks (6)

DAL_60_01
Pinus 1x1 to 6x4 (47)
blanks (6)

DAL_110_01
Pinus (11)
blanks (6)

DAL_110_02
Pinus (21)
blanks (6)

DAL_150_03-09
Pinus (7)

Cor_ave 14B1 skip 1x2 quadrant

DAL_08_01
Pinus (7)
blanks (4)

DAL_08_02
Pinus (2)
blanks (4)

DAL_08_03
Pinus (2)

DAL_40_01
Pinus 1x1 to 2x6 (37)
blanks (5)

DAL_08_04-15
Pinus (12)

DAL_140_01_17
Pinus (17)
